Asymmetric relationships and their effects on coexistence

### 2023-02-27 paper/Paper.Rnw
trivial
small adjustments to control flow for getting SEs and putting them into the paper

#place R code here for loading in necessary variables from Results
res_loc <- "../results_numeric/"
#fig2 <- readRDS(file=paste0(res_loc,"fig2data.RDS"))
M <- readRDS(file=paste0(res_loc,"M.RDS"))
se3 <- readRDS(file=paste0(res_loc,"fig3maxse.RDS"))
#se4 <- readRDS(file=paste0(res_loc,"fig4maxse.RDS"))
se4<-NA
se5 <- readRDS(file=paste0(res_loc, "fig5maxse.RDS"))
se6 <- readRDS(file=paste0(res_loc, "fig6maxse.RDS"))
@

@@

%Lottery model and results based on it
To further demonstrate the plausibility of ATAs altering coexistence between species, we carried out 
simple simulations using a two-species model, the well-known lottery model. The simulations described in this
paragraph are sufficient to demonstrate that ATAs influence coexistence in some manner; the
precise nature of that influence is the subject of the rest of the paper.
The lottery model is as follows.
Letting $N_i(t)$ denote the population density of species $i=1,2$ at time $t$, and defining $N = N_1(t)+N_2(t)$,
model equations are
\begin{equation}
N_i(t+1)=(1-\delta)N_i(t)+\delta N \frac{B_i(t)N_i(t)}{B_1(t)N_1(t)+B_2(t)N_2(t)}  \label{model_eq}
\end{equation}
for $i=1,2$. Here, $\delta$ is a mortality rate, and $B_i(t)$ is the fecundity of species $i$ at time $t$. 
The model postulates that individuals die at rate $\delta$ at each time step, and are replaced by juveniles 
in proportion to the reproductive outputs of the two species that year. Note that $N$ is constant through time. 
Notation for the whole paper is summarized in Table X.
%***DAN: make the table
For each $i$, we assume for simplicity that the random variables $B_i(t)$ are independent and identically 
distributed (iid) through time. In three distinct similations (Fig. \ref{fig:pedagog1}d-f), 
$B_1$ and $B_2$ were, respectively, 
left- (Fig. \ref{fig:pedagog1}a), right- (Fig. \ref{fig:pedagog1}c) and symetrically (Fig. \ref{fig:pedagog1}b)
tail associated, while the same marginal distributions for these fecundities were used in all simulations (see Methods
for details). Thus, the model setup was identical in the three simulations except for different ATAs. 
ATAs substantially influenced aspects of species coexistence in these simulations (Fig. \ref{fig:pedagog1}d-f).

@@

%***DAN: Jasmin, panel labels(a, b, c, etc.) need to be added. Please use the same format for these labels
%as you do in the other figures.
\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/decompFigLB.pdf}
\caption{The contribution of ATAs to species coexistence was often meaningfully large compared to 
other components of the MCT decomposition for the beta fecundities lottery model.
All panels show GWR and the decomposition of
GWR provided by the extended MCT, equation (\ref{eq:full_decomp}). For each panel,
$\delta$ is fixed at the value specified in the upper margin, 
and GWR and components of the decomposition
are plotted against $\eta_2/\eta_1$. The contribution of ATAs ($\Delta_i^{[EC]}$) frequently 
has magnitude comparable to other components, indicating that ATAs can contribute meaningfully
to species coexistence or failure to coexist. In some instances, the GWR line falls 
between the ATA line and the $x$ axis, indicating that, for those parameter values, ATAs make 
the difference between species
coexistence and exclusion of the weaker competitor. These instances, which are shaded, correspond to
ATA rescue or exclusion (Theory). Standard errors of plotted quantities 
were never greater than \Sexpr{round(NA,5)}, so are not displayed. 
%***DAN: Jasmin, we need to replace the NA in the above line by a variable names, which your code should have saved.
%The variable needs to be loaded in the R chunk near the top of this file, and then refereced here, please.
This plot uses $q_{ij}=1$. 
%***DAN: Right, Jasmin?
An analogous plot (SI Fig. \ref{SI-fig:fig4_alt}) was generated 
using $q_{ij}=\eta_i/(\eta_j(1-\delta)+\eta_i \delta)$. 
%***DAN: Jasmin, I believe the code does not produce the alternate-qij plot yet, but eventually it needs to.
Though results differed in detail, main conclusions were the same.
%***DAN: make sure this is indeed the case once the plot is generated.
}\label{fig:fig4}
\end{figure}

>>>>

#place R code here for loading in necessary variables from Results
res_loc <- "../results_numeric/"
#fig2 <- readRDS(file=paste0(res_loc,"fig2data.RDS"))
M <- readRDS(file=paste0(res_loc,"M.RDS"))
se3 <- readRDS(file=paste0(res_loc,"fig3maxse.RDS"))
se4 <- readRDS(file=paste0(res_loc,"fig4maxse.RDS"))
se5 <- readRDS(file=paste0(res_loc, "fig5maxse.RDS"))
se6 <- readRDS(file=paste0(res_loc, "fig6maxse.RDS"))
@

@@

%Lottery model and results based on it
To further demonstrate the plausibility of ATAs altering coexistence between species, we carried out 
simple simulations using a two-species model, the well-known lottery model. The simulations described in this
paragraph are sufficient to demonstrate that ATAs influence coexistence in some manner; the
precise nature of that influence is the subject of the rest of the paper.
The lottery model is as follows.
Letting $N_i(t)$ denote the population density of species $i=1,2$ at time $t$, and defining $N = N_1(t)+N_2(t)$,
model equations are
\begin{equation}
N_i(t+1)=(1-\delta)N_i(t)+\delta N \frac{B_i(t)N_i(t)}{B_1(t)N_1(t)+B_2(t)N_2(t)}  \label{model_eq}
\end{equation}
for $i=1,2$. Here, $\delta$ is a mortality rate, and $B_i(t)$ is the fecundity of species $i$ at time $t$. 
The model postulates that individuals die at rate $\delta$ at each time step, and are replaced by juveniles 
in proportion to the reproductive outputs of the two species that year. Note that $N$ is constant through time. 
Notation for the whole paper is summarized in Table X.
%***DAN: Dan to make the table
For each $i$, we assume for simplicity that the random variables $B_i(t)$ are independent and identically 
distributed (iid) through time. In three distinct similations (Fig. \ref{fig:pedagog1}d-f), 
$B_1$ and $B_2$ were, respectively, 
left- (Fig. \ref{fig:pedagog1}a), right- (Fig. \ref{fig:pedagog1}c) and symetrically (Fig. \ref{fig:pedagog1}b)
tail associated, while the same marginal distributions for these fecundities were used in all simulations (see Methods
for details). Thus, the model setup was identical in the three simulations except for different ATAs. 
ATAs substantially influenced aspects of species coexistence in these simulations (Fig. \ref{fig:pedagog1}d-f).

@@

%***DAN: Jasmin, panel labels(a, b, c, etc.) need to be added. Please use the same format for these labels
%as you do in the other figures.
\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/decompFigLB.pdf}
\caption{The contribution of ATAs to species coexistence was often meaningfully large compared to 
other components of the MCT decomposition for the beta fecundities lottery model.
All panels show GWR and the decomposition of
GWR provided by the extended MCT, equation (\ref{eq:full_decomp}). For each panel,
$\delta$ is fixed at the value specified in the upper margin, 
and GWR and components of the decomposition
are plotted against $\eta_2/\eta_1$. The contribution of ATAs ($\Delta_i^{[EC]}$) frequently 
has magnitude comparable to other components, indicating that ATAs can contribute meaningfully
to species coexistence or failure to coexist. In some instances, the GWR line falls 
between the ATA line and the $x$ axis, indicating that, for those parameter values, ATAs make 
the difference between species
coexistence and exclusion of the weaker competitor. These instances, which are shaded, correspond to
ATA rescue or exclusion (Theory). Standard errors of plotted quantities 
were never greater than \Sexpr{round(se4,5)}, so are not displayed. 
%***DAN: Jasmin, we need to replace the NA in the above line by a variable names, which your code should have saved.
%The variable needs to be loaded in the R chunk near the top of this file, and then refereced here, please.
This plot uses $q_{ij}=1$. 
%***DAN: Right, Jasmin?
An analogous plot (SI Fig. \ref{SI-fig:fig4_alt}) was generated 
using $q_{ij}=\eta_i/(\eta_j(1-\delta)+\eta_i \delta)$. 
%***DAN: Jasmin, I believe the code does not produce the alternate-qij plot yet, but eventually it needs to.
Though results differed in detail, main conclusions were the same.
%***DAN: make sure this is indeed the case once the plot is generated.
}\label{fig:fig4}
\end{figure}
